\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[frenchlinks]{cleveref}
\usepackage{mathptmx} % Times New Roman Font
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5} % For social media icons

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\tabcolsep}{0in}

% Formatting Sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r} \small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------- RESUME STARTS HERE -----------

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Gaurab Chhetri}} \\[3pt]
    \small
    \begin{tabular}{c}
        San Marcos, TX $|$
        \faGithub\ \href{https://github.com/gauravfs-14}{gauravfs-14} $|$
        \faLinkedin\ \href{https://www.linkedin.com/in/gaurabchhetri/}{gaurabchhetri} $|$
        \faGlobe\ \href{https://gaurabchhetri.com.np}{gaurabchhetri.com.np} $|$
        \faEnvelope\ \href{mailto:contact@gaurabchhetri.com.np}{contact@gaurabchhetri.com.np} $|$
         +1 (512) 665-1264
    \end{tabular}
\end{center}

%----------- SKILLS -----------
\section{Technical Skills}
\resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages:} JavaScript, TypeScript, HTML, CSS, PHP, SQL, Python, R, C/C++, Markdown}
    \resumeSubItem{\textbf{Frameworks \& Tools:} React.js ,Next.js, React Native, Expo, Express.js, Node.js, REST APIs, MySQL, MongoDB, Prisma, Tailwind CSS, Git, GitHub, Linux, WordPress}
    \resumeSubItem{\textbf{Other Skills:} SEO, Digital Marketing, Data Analysis, Data Visualization, CloudFlare, Netlify, Domain Management, IT Support, System Administration, Graphic Design, Video Editing, Figma, GIMP, Canva}
\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\href{https://github.com/gauravfs-14/bhanai}{Bhanai Programming Language}}{}
    \resumeItemListStart
        \resumeItem{Developed \textbf{Bhanai}, a Nepali-inspired programming language with custom syntax and execution capabilities.}
        \resumeItem{Published the package on npm, enabling easy global installation and execution.}
    \resumeItemListEnd
    
    \resumeProjectHeading{\href{https://ait-lab.vercel.app}{AIT Lab Website}}{}
    \resumeItemListStart
        \resumeItem{Built an \textbf{academic research website} for Texas State University using Next.js with modern web development practices.}
        \resumeItem{Achieved a \textbf{95+ Lighthouse score} by optimizing SEO, accessibility, and performance.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://photos.app.goo.gl/wxw7pM8xo3CacDHM9}{Custom Raspberry Pi Computer}}{}
    \resumeItemListStart
        \resumeItem{Designed and assembled a \textbf{custom Raspberry Pi-based mini computer} for multi-purpose educational use.}
        \resumeItem{Configured for \textbf{penetration testing, Linux learning, and programming education}.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Undergraduate Research Assistant}{Oct 2024 – Present}
    \resumeItemListStart
        \resumeItem{Conducting \textbf{data visualization and machine learning} research using R and Python, processing and analyzing large datasets.}
        \resumeItem{Developing analytical tools and visualization dashboards to present complex research findings.}
        \resumeItem{Collaborating with faculty to publish research in academic conferences and journals.}
    \resumeItemListEnd
    
    \resumeSubheading{ComputeNepal}{Nepal}{Founder and Developer}{May 2021 – Present}
    \resumeItemListStart
        \resumeItem{Founded \href{https://computenepal.com}{ComputeNepal.com}, a tech learning platform with 200+ articles and interactive tools.}
        \resumeItem{Implemented SEO strategies, increasing organic traffic by \textbf{300\%} and enhancing website visibility.}
        \resumeItem{Developed multiple sub-platforms, including quizzes, tutorials, and programming challenges for learners.}
    \resumeItemListEnd

    \resumeSubheading{Satmarga Education Consultancy}{Pokhara, Nepal}{IT Officer}{Feb 2024 – Jul 2024}
    \resumeItemListStart
        \resumeItem{Managed the \href{https://satmargaeducation.com}{company website}, domain registration, and IT security protocols.}
        \resumeItem{Developed and executed \textbf{social media marketing campaigns}, increased 1000+ followers.}
        \resumeItem{Designed and optimized digital content, ensuring better outreach and customer interaction.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Publications}
\resumeSubHeadingListStart
    \resumeSubheading{\href{https://myrepublica.nagariknetwork.com/news/online-gaming-and-child-safety/}{Online Gaming and Child Safety}}{Nepal}{República}{Apr 16, 2023}
    \resumeItemListStart
        \resumeItem{Published an op-ed discussing the impact of online gaming on child safety and preventive measures.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- HONORS & AWARDS -----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
    \resumeSubheading{Best in Development/Coding - Hackacat Nano 2024}{San Marcos, TX}{Organized by: ACM AI @ TXST}{Nov 2024}
    \resumeItemListStart
        \resumeItem{Developed RUMI: An AI-powered roommate finder using React, Node.js, and OpenAI in just 7hours.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Bachelor of Science in Computer Science (GPA: 4.0) | Dean's List Receptionist}{Aug 2024 – May 2029}
\resumeSubHeadingListEnd

%----------- LANGUAGES -----------
\section{Languages}
\resumeSubHeadingListStart
    \resumeSubItem{English (Fluent), Nepali (Native), Hindi (Fluent)}
\resumeSubHeadingListEnd

\end{document}
