\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cleveref}
\usepackage{mathptmx} % Times New Roman Font
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5} % For social media icons

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\setlength{\tabcolsep}{0in}

% Formatting Sections
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r} \small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------- RESUME STARTS HERE -----------

\begin{document}

% Header
\begin{center}
    {{\fontsize{18pt}{22pt} \selectfont \textbf{Gaurab Chhetri}}} \\[3pt]
    \small
    \begin{tabular}{c}
        Austin, TX $|$
        \faGithub\ \href{https://github.com/gauravfs-14}{gauravfs-14} $|$
        \faLinkedin\ \href{https://www.linkedin.com/in/gaurabchhetri/}{gaurabchhetri} $|$
        \faGlobe\ \href{https://gaurabchhetri.com.np}{gaurabchhetri.com.np} $|$
        \faEnvelope\ \href{mailto:contact@gaurabchhetri.com.np}{contact@gaurabchhetri.com.np} $|$
         +1 (xxx) xxx-xxxx
    \end{tabular}
\end{center}


%----------- SKILLS -----------
\section{Skills}
\resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages:} JavaScript, TypeScript, Python, R, C/C++, HTML, CSS, SQL, PHP}
    \resumeSubItem{\textbf{Web/App Development:} React.js, Next.js, React Native, Node.js, Express.js, REST APIs, MongoDB, MySQL, Prisma, Tailwind CSS}
    \resumeSubItem{\textbf{Tools \& Platforms:} Git, GitHub, Vite, Netlify, Cloudflare, WordPress, Expo, Linux}
    \resumeSubItem{\textbf{Data \& Visualization:} RStudio, Pandas, GGplot, Leaflet.js, D3.js, Recharts, Chart.js, Data Cleaning, Dashboarding}
    \resumeSubItem{\textbf{Creative \& Other:} Figma, Canva, GIMP, SEO, System Administration, CLI Utilities, Documentation}
\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading{Bhanai Programming Language (\href{https://www.npmjs.com/package/bhanai}{npmjs.com/package/bhanai})}{}{Node.js, JavaScript, CLI Tools}{}
\resumeItemListStart
    \resumeItem{Designed and developed a Nepali-inspired programming language with a custom lexer, parser, and interpreter.}
    \resumeItem{Published as a globally installable NPM package, enabling CLI-based scripting.}
\resumeItemListEnd

\resumeSubheading{AIT Lab Website (\href{https://ait-lab.vercel.app}{ait-lab.vercel.app})}{}{Next.js, React.js, Tailwind CSS, Vercel}{}
\resumeItemListStart
    \resumeItem{Built a performant academic website for the AI in Transportation Lab at Texas State University.}
    \resumeItem{Achieved 90+ Lighthouse scores in SEO and performance audits.}
\resumeItemListEnd

\resumeSubheading{ComputeNepal (\href{https://computenepal.com}{computenepal.com})}{}{WordPress, SEO, Google Analytics, HTML/CSS, Hosting Tools}{}
\resumeItemListStart
    \resumeItem{Founded a technical education platform with 200+ articles and tools, reaching thousands of users.}
    \resumeItem{Increased monthly traffic by 300\% via technical SEO and engagement strategies.}
\resumeItemListEnd

\resumeSubheading{Texas Measles Dashboard (\href{https://measles-dashboard.vercel.app}{measles-dashboard.vercel.app})}{}{Next.js, Leaflet.js, JavaScript, TypeScript, Python, CSV Parsing}{}
\resumeItemListStart
    \resumeItem{Built an interactive dashboard to visualize measles outbreaks across Texas counties using DSHS, TX datasets.}
    \resumeItem{Enabled dynamic filtering, responsive popups, and map overlays for policy visualization.}
\resumeItemListEnd

\resumeSubheading{TRBAM Bluesky Dashboard (\href{https://trbam-bluesky-dashboard.vercel.app}{trbam-bluesky-dashboard.vercel.app})}{}{Next.js, React.js, Bluesky API, Tailwind CSS, SQLite, Drizzle ORM, Vercel}{}
\resumeItemListStart
    \resumeItem{Created a dashboard to track TRBAM-related discussions using Bluesky's decentralized social data.}
    \resumeItem{Added filtering and sorting tools for researchers to analyze post trends during the conference.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Undergraduate Research Assistant}{Oct 2024 – Present}
    \resumeItemListStart
        \resumeItem{Developed 25+ analytical and visualization tools to improve data interpretation for AI-driven transportation research.}
        \resumeItem{Analyzed large datasets (150k+ entries) using JavaScript, R, and Python to draw meaningful insights from the data.}
        \resumeItem{Contributed to 6+ academic papers by conducting in-depth data analysis, figure preparation, visualization, and technical writing.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{Texas State University}{San Marcos, TX}{Bachelor of Science in Computer Science (GPA: 4.0) | Dean's List (Fall 2024–Present)
}{Expected May 2028}
\resumeSubHeadingListEnd


%----------- HONORS & AWARDS -----------
\section{Honors \& Awards}
\resumeSubHeadingListStart
    \resumeSubheading{Best in Development/Coding - Hackacat Nano 2024}{San Marcos, TX}{Organized by: ACM AI @ TXST}{Nov 2024}
    \resumeItemListStart
        \resumeItem{Developed RUMI: An AI-powered roommate finder using React, Node.js, and OpenAI in just 7 hours.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Publications}
\resumeSubHeadingListStart
    \resumeSubheading{\href{https://myrepublica.nagariknetwork.com/news/online-gaming-and-child-safety/}{Online Gaming and Child Safety}}{Pokhara, Nepal}{ 
    Read @ 
    \href{https://myrepublica.nagariknetwork.com/news/online-gaming-and-child-safety/}{República - The Partner of New York Times}}{Apr 2023}
\resumeSubHeadingListEnd

\end{document}
